---
title: "Iris"
author: "Sean"
format: html
editor: visual
---

This is a R code to visualization iris dataset. It splits the data into three subplot by Species.

___

**Step-by-step Explanation**

## 1. Load Required Library
```{r}
library(ggplot2)
```

- `ggplot2` is a package for drawing charts in R
- `library()` is a function to read a package

___

## 2. Create an Intital Scatter plot
```{r}
  iris_plot <- ggplot(iris, aes(x=Sepal.Length, y = Sepal.Width))+
  geom_point() +
  facet_grid(. ~ Species)
```
- `geom_point` :
  - Draw a scatter plot
- `facet_grid(. ~ Species)` :
  - Splits the plot into seperate panels for each `Species`
  
___
## 3. Create a Data Frame for Custom Labels
```{r}
g_labels <- data.frame(Species = c("setosa", "versicolor", "virginica"), 
                       label=c("Setosa", "Versicolor", "Virginica"))
```
- `g_labels` :
   - A data frame that contains custom labels(`label`) for each `species`

___

   
## 4. Add Custom Labels to The Plot
```{r}
#| output: false
iris_plot +
  geom_text(x = 7, y = 4, aes(label = label), data = g_labels)
```

-`geom_text(...)` :

  - Adds text labels to the plot.
- `x = 7` , `y = 4` :

  - Specifies the position for the labels in each facet.
- `aes(label = label)`: 

  - Maps the `label`   column from `f_labels`  to the text labels.
  
___ 

  
    
## 5. Add title and Axis Labels
```{r}
#| output: false
  labs(title = "Iris",
       x = "Sepal length",
       y = "Sepal width",
       caption = "By Sean, Data Visualization course, Tunghai University, 2024")+
  theme(plot.title = element_text(hjust = 0.5, size = 20))
```
-`labs(...)` 

  - Sets the plot's title(`title`), x-axis label(`x`), y-axis(`y`), and caption (`caption`)
  
___ 
  
  

## 6. Customize Plot Theme
```{r}
#| output: false
   theme(plot.title = element_text(hjust = 0.5, size = 20))
```
-`theme(...)` : 

- Modifies visual properties of the plot.

- `plot.title = element_text(hjust = 0.5, size = 20)`:

  - Centers the title (hjust = 0.5).
  - Increases the title font size to 20.

___ 

## 7. Complete Code & Result
```{r}

library(ggplot2)
  iris_plot <- ggplot(iris, aes(x=Sepal.Length, y = Sepal.Width))+
  geom_point() +
  facet_grid(. ~ Species)
```
```{r}
g_labels <- data.frame(Species = c("setosa", "versicolor", "virginica"), 
                       label=c("Setosa", "Versicolor", "Virginica"))
```
```{r}
iris_plot +
  geom_text(x = 7, y = 4, aes(label = label), data = g_labels) +
  labs(title = "Iris",
       x = "Sepal length",
       y = "Sepal width",
       caption = "By Sean, Data Visualization course, Tunghai University, 2024")+
  theme(plot.title = element_text(hjust = 0.5, size = 20))
```
##